Combining information from photometric and spectroscopic data:\\ Probabilistic spectrophotometric inference

### 2015-05-12 tex/ms.tex
change title

\begin{document}\sloppy\sloppypar
\title{Combining information from photometric and spectroscopic data:\\
  propogating uncertainties in spectrophotometric calibration}
\shorttitle{Combining Spectroscopy and Photometry}
\author{
  BDJ\altaffilmark{\lick},
  DRW\altaffilmark{\lick},
  DFM\altaffilmark{\ccpp},
  DWH\altaffilmark{\ccpp, \cds, \mpia},
  CC\altaffilmark{\lick},
  others}
\shortauthors{bdj et al}
\altaffiltext{\lick}{University of California Lick Observatory}
\altaffiltext{\ccpp}{Center for Cosmology and Particle Physics, Department of Physics, New York University}
\altaffiltext{\cds}{Center for Data Science, New York University}
\altaffiltext{\mpia}{Max-Planck-Institut f\"ur Astronomie}

\begin{abstract}
In a typical spectral-fitting project,
  there tend to be a small number of bands of well-calibrated photometry
  and thousands of poorly calibrated spectroscopic pixels.
Good spectroscopic calibration is both expensive and difficult,
  but naive weighted least-square fitting will weight
  the thousands of spectroscopic pixels far higher overall
  than the few photometric bands.
Here we present a flexible and general spectroscopic calibration model,
  which can be fit simultaneously along with whatever spectral parameters.
The model involves a polynomial calibration vector to capture large-scale calibration issues
  and a Gaussian Process to capture small-scale wiggles.
We show that, in this framework, the quality of some kinds of spectral parameter fits
  is not a strong function of the quality of the spectroscopic calibration;
  that is, for many scientific goals there is no scientific reason
  to obtain good---or really any---spectrophotometric calibration.
In particular, for stellar population fitting, high signal-to-noise data,
  and good photometry,
  we show that raw counts are just as good as calibrated counts for making inferences about the
  parameters of interest.
This obviation of calibration overheads will pay \emph{all yall mad cheddar},
  at least if yall employ full cost accounting.
\end{abstract}

>>>>

\begin{document}\sloppy\sloppypar
\title{Combining information from photometric and spectroscopic data:\\
  Probabilistic spectrophotometric inference}
\shorttitle{Combining Spectroscopy and Photometry}
\author{
  BDJ\altaffilmark{\lick},
  DRW\altaffilmark{\lick},
  DFM\altaffilmark{\ccpp},
  DWH\altaffilmark{\ccpp, \cds, \mpia},
  CC\altaffilmark{\lick},
  others}
\shortauthors{bdj et al}
\altaffiltext{\lick}{University of California Lick Observatory}
\altaffiltext{\ccpp}{Center for Cosmology and Particle Physics, Department of Physics, New York University}
\altaffiltext{\cds}{Center for Data Science, New York University}
\altaffiltext{\mpia}{Max-Planck-Institut f\"ur Astronomie}

\begin{abstract}
In a typical spectral-fitting project,
  there tend to be a small number of bands of well-calibrated photometry
  and thousands of poorly calibrated spectroscopic pixels.
Good spectroscopic calibration is both expensive and difficult,
  but naive weighted least-square fitting will weight
  the thousands of spectroscopic pixels far higher overall
  than the few photometric bands.
Here we present a flexible and general spectroscopic calibration model,
  which can be fit simultaneously along with whatever spectral parameters.
The model involves a polynomial calibration vector to capture large-scale calibration issues
  and a Gaussian Process to capture small-scale wiggles.
We show that, in this framework, the quality of some kinds of spectral parameter fits
  is not a strong function of the quality of the spectroscopic calibration;
  that is, for many scientific goals there is no scientific reason
  to obtain good---or really any---spectrophotometric calibration.
In particular, for stellar population fitting, high signal-to-noise data,
  and good photometry,
  we show that raw counts are just as good as calibrated counts for making inferences about the
  parameters of interest.
\end{abstract}
